%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{Ashton}{Kemerling}{ \urlstyle{same}\url{https://ashtonkemerling.com} \\
\href{mailto:ashton.kemerling@protonmail.com}{ashton.kemerling@protonmail.com} | 312.582.0313
}

\href{https://www.linkedin.com/in/ashton-kemerling/}{https://www.linkedin.com/in/ashton-kemerling/}

\begin{center}
\end{center}

\section{Experience - Management}

\runsubsection{Hulu/Disney}
\descript{| Engineering Manager }
\location{2020 - Current | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
I've managed two teams at Disney, with a total of thirteen direct reports. Both teams were responsible for high-visibility client facing features such as pause/resume, the Hulu Cloud DVR, and Continue Watching. After a recent re-org, I was specifically selected for my current team as the best manager to represent our division to external stakeholders and fellow engineering team leads. This team is critical for the ongoing ``unification'' of all Disney streaming brands into one unified technical architecture.
\vspace{\topsep}
\newline
Key Deliverables
\begin{tightemize}
\item Successfully replaced legacy Disney+ pause/resume system, saving \$36m per year.
\item Cut Hulu Cloud DVR cost by 75\%.
\item Technical lead for a successful multi-team, multi-discipline initiative to launch unlimited DVR for Hulu.
\item First team to deliver production features for the new, unified Disney Streaming technical architecture.
\item Replaced multiple single purpose applications with a single app for all user content preferences.
\item Migrated all applications from on-premise to cloud native alternatives ahead of schedule.
\item First incident free Super Bowl for the DVR in Hulu history.
\end{tightemize}

\sectionsep
People Management
\begin{tightemize}
\item Increased headcount by 40\%, allowing the team to divide and increase scope.
\item Successfully trained two individual contributors to become managers.
\item Mentored three software engineers into senior level positions on the IC track.
\item Led team through an unexpected transition to remote work.
\item Maintained lowest attrition rate in the division.
\end{tightemize}
\sectionsep

Cross Team Impact
\begin{tightemize}
\item Closely collaborated with multiple product owners and technical stakeholders for Unlimited DVR.
\item Continued work with multiple teams to deliver features for the onging unification project.
\item Managed QA efforts for the division during major, public feature releases.
\item Oversaw creation of cross-team best-practices committee to improve technical quality and efficiency.
\end{tightemize}
\sectionsep

\runsubsection{Edmunds.com}
\descript{| Engineering Manager }
\location{2017 - 2019 | Santa Monica, CA}
\vspace{\topsep}
Responsible for the ``Lead Systems'' team. This team managed the entire stack for collecting customer leads and delivering them to both dealerships and OEMs from the form to final delivery. This system was critical for 30\% of Edmunds total revenue, and required us to meet the requirements of both OEM and dealership stakeholders.
\vspace{\topsep}
\newline
Key Deliverables
\begin{tightemize}
\item Planned and executed the migration of a dozen lead forms to a single one based on React.
\item Maintained a unified lead form used on multiple pages with different product owners.
\item Designed and released a number of internal tools to enable rapid iteration of lead form designs.
\item Created a series of self service tools, eliminating support requests from product owners.
\item Designed a system for protecting customer data in close collaboration with Data Analytics.
\item Worked closely with Business Development to deliver features requested by OEMs on short time schedules.
\end{tightemize}

\sectionsep
People Management
\begin{tightemize}
  \item Redesigned and unified the hiring process for all backend engineers.
  \item Only non-executive engineering representative on the hiring committee.
  \item Created a new title scheme for all engineers, providing clearer expectations and growth paths.
\end{tightemize}

\pagebreak

\section{Experience - Engineering}

\runsubsection{DRW Trading}
\descript{| Senior Software Engineer}
\location{2015 - 2017 | Chicago, IL}
\vspace{\topsep}
One of a small team responsible for maintaining a key middle layer in all DRW trading operations. The applications we ran maintained a record of every financial instrument the company traded across multiple exchanges, as well as maintain the ongoing trades and positions of every independant trading desk within the company. We also ran a high performance system for streaming trades and positions in real time to excel for analyst usage, as well as a few special purpose applications to enable necessary back office functions.
\vspace{\topsep}
\begin{tightemize}
\item Worked on the team that maintained the company's trade \& position store and the trading instrument reference application.
\item Completed rewrite of the process to import financial futures for better performance and reliability.
\item Wrote an application analyzing bond interest, providing better accuracy than a Bloomberg terminal.
\item Helped maintain system uptime even during the record breaking trading days of Brexit and the 2016 election.
\item Wrote multiple services to automated end of day back end processes, saving dozens of hours of labor per week.
\item Expanded and improved open source and internal devops tools.
\item Administered over 100 internal servers and VMs.
\item Maintained and improved existing Excel add-ons, written in C\#.
\item Maintained trade critical systems in Ruby, Java, Clojure, C\#, and Javascript.
\end{tightemize}
\sectionsep

\runsubsection{Pivotal Labs}
\descript{| Software Engineer}
\location{2013 - 2015 | Denver, CO}
\vspace{\topsep}
Full stack engineer for one of Pivotal Lab's only B2C offerings, Pivotal Tracker.
\vspace{\topsep}
\begin{tightemize}
\item Used generative testing to find reliable reproduction steps for both long running bugs, and new bug reports.
\item Diagnosed and resolved a memory leak in Chrome, reducing memory usage by an order of magnitude.
\item Finished years long migration from Rails 2 to Rails 3, including porting documentation critical rspec patches.
\item Completed years long rewrite of the SPA front end, including cleaning up the git history.
\item Introduced React to Pivotal Tracker, to replace increasingly hard to maintain backbone.js code base.
\end{tightemize}

\sectionsep
\runsubsection{Narrative Science}
\descript{| Software Engineer}
\location{2012 - 2013 | Chicago, IL}
\vspace{\topsep}
\begin{tightemize}
\item Sole engineer for company's only public facing product, Quill for Google Analytics.
\item Maintained ELT \& ETL pipelines in Python for multiple clients.
\item Rewrote one-off data processing scripts to use a consistent structure for long term maintenance.
\item Led company wide effort to migrate to immutable infrastructure for better reliability and reduced cost.
\item Reworked CI/CD infrastructure for faster builds at half the cost.
\end{tightemize}

\sectionsep
\runsubsection{OnShore Development}
\descript{| Intern \& Junior Software Engineer}
\location{2011 - 2012 | Chicago, IL}
\vspace{\topsep}
\begin{tightemize}
\item Maintained primary application written in Common Lisp.
\item Helped rewrite core algorithms to reduce processing time from minutes to seconds.
\item Replaced custom Perl deployment scripts with Chef.
\item Created in house i8n library to translate the application for international customers for the first time.
\end{tightemize}

\section{Education}
\runsubsection{Loyola University Chicago}
\descript{| BS in Computer Science}
\location{2012 | Chicago, IL}
\sectionsep

\runsubsection{Loyola University Chicago}
\descript{| BS in Mathematics}
\location{2012 | Chicago, IL}
\sectionsep


%% \section{Languages}
%% \begin{minipage}[t]{.6\textwidth}
%% \subsection{Programming}
%% \location{Over 5000 lines:}
%% Java \textbullet{}   Shell \textbullet{} JavaScript \textbullet{} Matlab \textbullet{}
%% OCaml \textbullet{} Python \textbullet{} Rails \textbullet{} \LaTeX\ \\
%% \location{Over 1000 lines:}
%% C \textbullet{} C++ \textbullet{} CSS \textbullet{} PHP \textbullet{} Assembly \\
%% \location{Familiar:}
%% AS3 \textbullet{} iOS \textbullet{} Android \textbullet{} MySQL
%% \sectionsep
%% \end{minipage}
%% \hfill
%% \begin{minipage}[t]{.35\textwidth}
%% \subsection{Spoken \& Written}
%% \location{Native fluency:} English, Spanish\\
%% \location{Reading fluency:} Chinese, Japanese\\
%% \end{minipage}

\end{document}  \documentclass[]{article}
